---
format: revealjs
---

## Today's Agenda {background-image="Images/background-forest_v3.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)
```

<br>

::: {.r-fit-text}

**Section 2: Historical Perspectives on Wilderness**

:::

- Reflecting on the sublime narratives in our markets and politics

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. ...

<br>

**SLIDE**: I only see you guys twice a week, so let's speed through how we've gotten to this point

:::



## {background-image="Images/background-forest_v3.png" .center}

::: {.r-fit-text}
**A Spectrum of Environments (Nash 2014)**
:::

<br>

```{r, fig.align = 'center', fig.width = 6, fig.height=1.25}
## Manual DAG
d1 <- tibble(
  x = c(-3, 3),
  y = c(1, 1),
  labels = c("Purely\nCivilized", "Purely\nWild")
)

ggplot(data = d1, aes(x = x, y = y)) +
  geom_point(size = 8) +
  theme_void() +
  coord_cartesian(xlim = c(-4, 4)) +
  geom_label(aes(label = labels), size = 7) +
  annotate("segment", x = -1.9, xend = 1.9, y = 1, yend = 1, arrow = arrow(ends = "both"))
```

::: notes

**Refresh my memory, what is the big picture Nash wants us to accept about wilderness?**

<br>

The wilderness is not a "thing," it is a quality.

- All environments can be placed on a scale from complete human control to the absence of direct human control

<br>

**SLIDE**: We took that argument to 


:::























## For Next Class {background-image="Images/background-forest_v3.png" .center}

<br>


::: notes

<br>

**Questions on the assignment?**

:::